---
title: "assignment2"
author: "Daniel Vogel"
date: "1/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 2: Beaver Body Temperatures

The built in dataframe, **beaver1**, tracks the body temperature of a beaver over approximately 20 hours in 10 minute intervals.
There are 4 columns: *day*, *time*, *temp*, *activ*

The date=346.0 for all data so these observations were done on a single day.
The time is a range of 0..2350 which represents hour:minutes but after midnight, time time resets to 0.
The activ field is just: activ=1 or activ=0

### Summary beaver1
```{r beaver1, echo=FALSE}
summary(beaver1)
print("The first 5 entries")
head(beaver1,n=5)
print("The last 5 entries")
tail(beaver1,n=5)
```

## Plotting the Temp Column
>This was alot harder than I expected!  
Since the "time" column in the beaver1 dataframe goes from 840..2350..0..340, it is not possible to simply plot time,temp.
You would have to convert time into a sequence of numbers that increases.  

Instead, I used the observation# as the x axis. This is not explicitly a column in beaver1. 
The x-axis was created with a vector x from 1..#observations.  i.e. 1 2 3. ..114
For the y-axis used the "temp" column from the beaver1 dataframe.  

>DANGER Will Rogers!!

This does not work if you use the syntax:  y<-beaver1["temp"] 

Plot spits out an error, **"Error in xy.coords(x, y, xlabel, ylabel, log) :  'x' and 'y' lengths differ"**

This is because "x" is a vector class and the "y" column is a sub-dataframe. Plot needs x,y to be the same type.  
To create the y-axis, use the [[*]*column*] syntax.  i.e.  y<-beaver1[["temp"]]
The [[]] converts the column to a vector.  Now x,y are both vector type. 

The command to plot is then:
plot(x,y,type="l")

```{r beaver1Plot, echo=FALSE}
observations<-nrow(beaver1)
print(paste("Observations:",observations))
x<-1:observations
y<-beaver1[["temp"]]
plot(x,y,type="l")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
